The role of aneuploidy in the evolution of cancer drug resistance

### 2023-06-04 EvolutionaryRescue1.tex
change title
update figure

% Title page
\title{Modeling the effect of aneuploidy on cancer evolution}
% Authors
\renewcommand\Affilfont{\small}

@@

The ratio of rescue probability with and without aneuploid ($H$, \cref{ratiorescue}) increases with the aneuploid growth rate (colors) and decreases with the wildtype growth rates and initial tumor size (x-axis), except for large tumors where aneuploid cells are tolerant (see right side of panel B-right). 
\textbf{(A-left,A-right)} Aneuploidy provides partial resistance. \textbf{(B-left, B-right)} Aneuploidy provides tolerance.  

@@

>>>>

% Title page
\title{The role of aneuploidy in the evolution of cancer drug resistance}
% Authors
\renewcommand\Affilfont{\small}

@@

The ratio of rescue probability with and without aneuploid ($H$, \cref{ratiorescue}) increases with the aneuploid growth rate (colors) and decreases with the wildtype growth rates and initial tumor size (x-axes), except for large tumors where where the ratio converges to unity.
\textbf{(A-left,A-right)} Aneuploidy provides partial resistance.
\textbf{(B-left, B-right)} Aneuploidy provides tolerance.  

@@

% TODO start y at 1
